Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-08-11 paper/main.tex
[issue 1.3] include multilayer perceptron

Deep learning is a rapidly developing field, and recent developments include
improved network architectures.
For future work, we plan to train more ConvNet variants, such as the
Inception Module~\citep{szegedy2015going} and Residual Network~\citep{he2015deep}.
To improve the predictive performance,
we have combined the predictions of different models across multiple
transformations of the input images (Section~\ref{sec:bmc}).
To further improve the performance, we could also train several networks
with different architectures and combine the models.
For example, the winning solution of \cite{dieleman2015rotation}
for the Galaxy Zoo challenge was based on a ConvNet model,
and it required averaging many sets of predictions from models with different
neural network architectures.

@@

>>>>

Deep learning is a rapidly developing field, and recent developments include
improved network architectures.
For future work, we plan to train more ConvNet variants, such as the
Inception Module~\citep{szegedy2015going} and Residual Network~\citep{he2015deep}.
To improve the predictive performance,
we have combined the predictions of different models across multiple
transformations of the input images (Section~\ref{sec:bmc}).
To further improve the performance, we could also train several networks
with different architectures and combine the models.
For example, the winning solution of \cite{dieleman2015rotation}
for the Galaxy Zoo challenge was based on a ConvNet model,
and it required averaging many sets of predictions from models with different
neural network architectures.
\changed{
Futhermore, future work could compare the performance of other deep learning
variants, such as deep belief networks~\citep{hinton2006fast},
deep Boltzmann machines~\citep{salakhutdinov2009deep}, and
multilayer perceptrons~\citep{wasserman1988neural}.
}

@@

\changed{
Finally, we are currently exploring different strategies for including objects
that are neither stars nor galaxies (\eg quasars).
The results of this multi-class problem will be presented in subsequent papers.
}
